A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period

### 2021-06-22 analysis/paper/paper.Rmd
replace code for caching the models with code that reads their outputs

```{r bergm-pre, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/code/003-burials-post-network-modelling.R"))}
suppressWarnings(source(here::here("analysis", "code", "003-burials-pre-network-modelling.R")))
```

```{r bergm-post, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/code/004-burials-post-network-modelling.R"))}
suppressWarnings(source(here::here("analysis", "code", "004-burials-post-network-modelling.R")))
```

>>>>

```{r read-models-data, include=FALSE}
load(here::here("analysis", "data", "derived_data", "burial_bergm_model.RData"))
readRDS(here::here("analysis", "data", "derived_data", "pre_bergm.rds"))
readRDS(here::here("analysis", "data", "derived_data", "post_bergm.rds"))
```
